Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-19 article.tex
more edits to history

\section{History}
Molecules consist of various atoms and the elementary unit of an atom is electron and nucleus. When we consider atomic energy, electron-nuclei,
electron-electron interactions must be examined. Molecular energy consists of interactions between multiple atoms, including interactions between
 electrons from different atoms, as well as nuclei. Molecular energy can be pictured as a large package that contains many small balls, and the
 sum of the energy of their collisions is the sum of interactions between atoms.

>>>>

\section{History}
Molecules are composed of collections of atoms, and the units that make up an atom are electrons and the atomic nucleus. When we consider the
 atomic energy then we must take into account both electron-nuclei and electron-electron interactions. The molecular energy consists of interactions
 between multiple atoms, and interactions between electrons from different nuclei. Molecular energy can be pictured as a large
 package that contains many small balls, and the sum of the energy of their collisions is the sum of interactions between atoms.
